The ANTs Cortical Thickness Pipeline

### 2013-02-08 SPIE2013/KK/Presentation/presentation.tex
ENH:  Updating.

\documentclass[xcolor=dvipsnames,serif,10pt]{beamer}

\usepackage{beamerthemesplit}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
%\usefonttheme{professionalfonts}
%\usepackage{times}
\usepackage{tikz}
\usepackage{amsmath,cancel}
\usepackage{mathtools}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usepackage{listings}
\usepackage[]{geometry}
\usepackage{ifxetex}
\ifxetex{%
  \usepackage{fontspec}
  \setmainfont{Linux Libertine O} % or any font on your system
  \newfontfamily\quotefont[Ligatures=TeX]{Linux Libertine O} % or any font on your system
\else
  \usepackage[T1]{fontenc}
  \usepackage{libertine} % or any other font package (or none)
  \newcommand*\quotefont{\fontfamily{fxl}} % selects Libertine for quote font
\fi
\usepackage{framed}

\usepackage{soul}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{calc,shapes.callouts,shapes.arrows}
\makeatletter

@@

% -My goal is to not get you excited about {\em my} research and the research I'm doing with
%  my collaborators.  Rather I want to get you excited about resources here at UVa for doing
%  {\em your} research, particularly if it involves computational image analysis and moderate
%  to large sized cohorts

\title[Big$\times$(Science $+$ Imaging) at UVA]{$\text{Big}\times(\text{Science}+\underbracket{\cancel{\text{Data}}}_{\small \text{Imaging}})$ @ UVA}
\author[N. Tustison]{%
  Nick Tustison, DSc
  }
\date[SOM Research Retreat]{}
\institute[ntustison@virginia.edu]{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  * PNAS VBM study of London cab drivers.
%%  * 465 data points age ~ 1 + cortical_atrophy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% (Transition)  Let's start off with an interesting study that was done about 10 years ago.

% These computational techniques have proven invaluable in exploring fundamental, and perhaps 
% not so fundamental, neuroscience questions.

\footnotesize

\begin{frame}{Hippocampal growth in London taxi drivers}

  \begin{columns}[c]
    \begin{column}{0.5\textwidth}
    \begin{center}  
      \includegraphics[width=5cm]{London_taxi.jpg}
    \end{center}
    \end{column}  
    \begin{column}{0.4\textwidth}
    \begin{center}  
      \vspace{-0.5cm}
      \pause
      \includegraphics[width=5cm]{hippocampus.png} \\
      \pause
        \begin{align*}
			  SPM (1995):\,\,&   6418\,\,\text{citations}\\
			  VBM (2000):\,\,&   3593\,\,\text{citations}\\
			  Opt. VBM (2001):\,\,&  2353\,\,\text{citations}\\
			  TBSS (2006):\,\,&  1106\,\,\text{citations}\\
			  \end{align*}
      \vspace{0cm}
			  \highlight[yellow!100!black]{$6418 + 3593 + 2353 + 1106 = 13470\,\,\text{citations}$}
    \end{center}
    \end{column}  
  \end{columns}    
\end{frame}

\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Studies at UVA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% (Transition)  Let's fast forward about 10 years to a young researcher at UVa who.
% Needless to say it was an interesting two year journey which finally ended in November
% when our paper was finally published in Human Brain Mapping which shows how these 
% techniques are susceptible to a methodological flaw known as logical circularity.

{
\usebackgroundtemplate{\includegraphics[width=1.175\paperwidth]{breachers.jpg}}%
\begin{frame}{TBI in breachers---{\em neuroimaging correlates?}}
   \begin{center}
   \vspace{0cm}
  \pause
   \color{black}{Investigate white matter injury \\
   {\scriptsize controls/students/instructors}} \\
   \vspace{1cm}
  \pause
   \color{black}{\em Logical circularity in\\ SPM, VBM, \& TBSS} \\
   \end{center}
\end{frame}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Make commands for the quotes
\newcommand*{\openquote}{\tikz[remember picture,overlay,xshift=-20pt,yshift=-5pt]
     \node (OQ) {\quotefont\fontsize{60}{60}\selectfont``};\kern0pt}
\newcommand*{\closequote}{\tikz[remember picture,overlay,xshift=-30pt,yshift=-10pt]
     \node (CQ) {\quotefont\fontsize{60}{60}\selectfont''};}
% select a colour for the shading

\begin{frame}{}
  \begin{center}

  \begin{columns}[c]
    \begin{column}{0.6\textwidth}
	    \begin{center}  
					\begin{shadequote}
					{\large {\em Maximum efficiency with minimum} wasted {\em effort}}.\par{Jigaro Kano$'$}
					\end{shadequote}
			\end{center}		
    \end{column}
    \hspace{-2.5cm}
    \begin{column}{0.2\textwidth}
		  \begin{center}
		    \includegraphics[height=4cm]{Kano_Jigoro.png}
		  \end{center}
		\end{column}  
  \end{columns}		
  \vspace{1cm}
  \pause
  {\LARGE \em There are \highlight[green, draw=blue]{life-altering} and \highlight[red!100!black]{free} UVA resources that you are probably not using!}
  \end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  What is data analysis? (neuroscience highlighted)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}

\tikzset{level 1 concept/.append style={font=\sf, sibling angle=135,level distance = 25mm}}
\tikzset{level 2 concept/.append style={font=\sf, sibling angle=60,level distance = 15mm}}
\tikzset{level 3 concept/.append style={font=\sf, sibling angle=60,level distance = 15mm}}
\tikzset{every node/.append style={scale=0.5}}

\begin{center}
\resizebox{9cm}{7.5cm}{
\begin{tikzpicture}
  \path[mindmap,concept color=red!50!black,text=white]
    node[concept,scale=0.9] {\Large Data Analysis}
    [clockwise from=45]
    child[concept color=green!50!black, yshift=-0.5cm] {
      node[concept,scale=1.1] {Imaging Applications}
      [clockwise from=120]
      child[concept color=green!80!black] { node[concept] (ns) {Neuro\-science} }
      child { node[concept] {Func. Lung Imaging} }
      child { node[concept] {Breast} }
      child { node[concept] {Cardiac} }
    }  
    child[concept color=blue!80!black, yshift=0.25cm] {
      node[concept,scale=1.1] (stat) {Statistics}
      [clockwise from=-60]
      child { node[concept] {Linear Modeling} }
      child { node[concept] (ml) {Machine Learning} }
    }
    child[concept color=orange, yshift=-0.5cm] { 
      node[concept,scale=1.1] {Computer Science} 
        [clockwise from=-145]
        child { node[concept] (ad) {Algorithm Development}
           [clockwise from=-60]
           child { node[concept] (antsr) {\footnotesize ANTsR} }
           child { node[concept] {ANTs} }
           child { node[concept] {ITK} }
           }
        child { node[concept] (cp) {Computer Programming} }
        child { node[concept] (cc) {Cluster Computing} }
    };

		\newcommand{\connbluetoorange}{to[circle connection bar switch color=from (blue!80!black) to (orange)]}
		\newcommand{\connorangetoorange}{to[circle connection bar switch color=from (orange) to (orange)]}
		\newcommand{\conngreentoorange}{to[circle connection bar switch color=from (green!80!black) to (orange)]}

  \begin{pgfonlayer}{background}
      \path (ad) \connorangetoorange (cp);
      \path (stat) \connbluetoorange (antsr);
      \path (ns) \conngreentoorange (cc);
  \end{pgfonlayer}

%  \begin{pgfonlayer}{background}
%      \path (ml) \connbluetoorange (cs);
%  \end{pgfonlayer}

\end{tikzpicture}
}
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Wintermark studies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{}
\setbeamercovered{invisible}

\tikzstyle{mybox} = [draw=black, fill=bottomcolour, thick,
    rectangle, rounded corners, inner sep=10pt, inner ysep=10pt]
\tikzstyle{mybox2} = [draw=black, fill=middlecolour, thick,
    rectangle, rounded corners, inner sep=5pt, inner ysep=5pt, 
    minimum height=4cm]
\tikzstyle{fancytitle} =[fill=bottomcolour, text=textcolour, rectangle]
\tikzstyle{line} = [-latex',very thick,textcolour]

%\begin{center}
%\begin{tikzpicture}
%};
%\end{tikzpicture}%
%\end{center}
%\vspace{5mm}

\begin{center}
\begin{tikzpicture}[node distance = 4cm]

\node [shift={(4cm,4cm)},mybox] (max){%
  Misc. neuroimaging projects};

\uncover<1->{
\node [mybox2, text width = 3.5cm, opacity = 1] (SkullThickness) {%  
  \begin{center}
  \begin{tabular}{c}
  \includegraphics[height=2cm]{skullThickness.png} 
  \vspace{0.25cm}
  \end{tabular}
  \scriptsize{Surrogate CT Skull Thickness Measurements with MRI}
  \end{center}
  };
\node[fancytitle] (SkullThickness_title) at (SkullThickness.north) {\scriptsize Skull Thickness};
\path[line] (max.south) edge [out= 230, in= 90] (SkullThickness_title.north);
}

\uncover<2->{
\node [mybox2, text width = 3.5cm, right of=SkullThickness] (ET) {%
  \begin{center}
  \begin{tabular}{c}
  \includegraphics[height=1.8cm]{ET.png} 
  \vspace{0.25cm}
  \end{tabular}
  \scriptsize{Longitudinal FA correlations following surgical treatment for ET}
  \end{center}
  };
\node[fancytitle](ET_title) at (ET.north) {\scriptsize Essential Tremor};
 \path[line] (max.south) edge [out= 270, in= 90] (ET_title.north);
 }

\uncover<3->{
\node [mybox2, text width = 3.5cm, right of=ET] (ASL) {%
  \begin{center}
  \begin{tabular}{c}
  \includegraphics[height=2.75cm]{ASL.png} 
  \vspace{0.15cm}
  \end{tabular}
  \scriptsize{Automatic generation of clinical CBF maps from ASL}
  \end{center}
  };
\node[fancytitle](ASL_title) at (ASL.north) {\scriptsize ASL$\rightarrow$CBF};
\path[line] (max.south) edge [out= 310, in= 90] (ASL_title.north);
}

%\begin{tikzpicture}
%  \tikz[overlay]\path[line] (max.south) edge [out= 230, in= 90] (SkullThickness_title.north);
%  \tikz[overlay]\path[line] (max.south) edge [out= 270, in= 90] (ET_title.north);
%  \tikz[overlay]\path[line] (max.south) edge [out= 310, in= 90] (ASL_title.north);
%\end{tikzpicture}
\end{center}

@@

\uncover<1->{
    \path[->,rounded corners=0.1cm] node[format, yshift=2cm, text width=1.5cm ] (ixi) { 
        \begin{center}
			  \includegraphics[height=1.75cm]{IXI221.png} \\
        \tiny{Input MRI}
        \end{center}
			  };
    \path[->] node[format, right of=ixi, xshift=0.5cm, text width=1.25cm] (n4) {
          \begin{center}
            \tiny{Initial N4 bias correction}
          \end{center}
        };
    \draw[->] (ixi.0) --  (n4.180);    
    \path[->] node[format, below of=n4, yshift = 1.25cm, text width=1.25cm] (be) {
          \begin{center}
            \tiny{Brain extraction}
          \end{center}
        };
    \draw[->] (n4.-90) -- (be.90);    
    \path[->] node[format, below of=be, yshift = 1.25cm, text width=1.25cm] (n4_2) {
          \begin{center}
            \tiny{N4 using WM estimate}
          \end{center}
        };
    \draw[->] (be.-90) -- (n4_2.90);    
    \path[->] node[format, below of=n4_2, yshift=1.25cm, text width=1.25cm] (atropos) {
          \begin{center}
            \tiny{3-tissue segmentation}
          \end{center}
        };
    \draw[->] (n4_2.-90) -- (atropos.90);    
    \path[->] node[diamond, draw, thick, fill=middlecolour, left of=atropos, xshift=1.75cm, yshift=0.875cm, text width=0.5cm] (conv) {
          \begin{center}
            \tiny{Conv.?}
          \end{center}
        };
    \draw[->] (atropos.180) -| (conv.270);    
    \draw[->] (conv.90) |- node {\tiny no} (n4_2.180);

    \path[->] node[format, left of=atropos, xshift=-0.5cm, text width=1.5cm ] (kk) {
        \begin{center}
        \tiny{Cortical thickness estimation}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[format, above of=kk, yshift=-1cm, text width=1.5cm ] (kkmap) {
        \begin{center}
			  \includegraphics[height=1.75cm]{IXI221_direct.png} \\
        \tiny{Thickness map}
        \end{center}
			  };

    \draw[->] (conv.180) -- node {\tiny yes} ([yshift=0cm,xshift=-0.45cm]conv.180) |- (kk.0);    
    \draw[<-] (kkmap.270) -- (kk.90);    
}

\uncover<2->{
    \path[->,rounded corners=0.1cm] 
      node[format, right of=n4, xshift=1.15cm, yshift=-2.5cm,text width=4.75cm] (template) { 
        \begin{center}
        \tiny{Oasis template (35 normals)}
        \begin{tabular}{cc}
          \includegraphics[width=1.5cm]{MICCAI_T1.png} &
          \includegraphics[width=1.5cm]{MICCAI_probMask.png} \\
          \tiny{T1} & \tiny{Whole brain} 
        \end{tabular} \\
        \begin{tabular}{ccc}
          \includegraphics[width=1.5cm]{MICCAI_probCSF.png} &
          \includegraphics[width=1.5cm]{MICCAI_probGM.png} &
          \includegraphics[width=1.5cm]{MICCAI_probWM.png} \\
          \tiny{CSF} & \tiny{GM} & \tiny{WM}
        \end{tabular} \\
        \end{center}
			  };
    \draw[->,dashed] (template.160) -- ([yshift=0cm,xshift=-0.5cm]template.160) |- (be.0); 
    \draw[->,dashed] (template.200) -- ([yshift=0cm,xshift=-0.5cm]template.200) |- (atropos.0); 
}

\uncover<3->{
  \node[decorate,draw,minimum height=7.25cm,minimum width=5.65cm,dashed,rounded corners=0.2cm, thin, color = yellow] (c) at (1.7,-0.35) {};
}  
\uncover<4->{
  \node[decorate,draw,minimum height=5.25cm,minimum width=5.55cm,dashed,rounded corners=0.2cm, thin, color = red] (c) at (7.7,-0.45) {};
}
\end{tikzpicture}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Open source software
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% - The visible human project (1999)---one of the earliest big imaging data/big science challenges.
%

\begin{frame}{Big data $\rightarrow$ open source software}

\begin{center}
\begin{tikzpicture}[node distance=3.5cm, auto,>=latex', thin]
    % We need to set at bounding box first. Otherwise the diagram
    % will change position for each frame.
    \path[use as bounding box] (-1,0) rectangle (10,0);

>>>>

\documentclass[xcolor=dvipsnames,serif,10pt]{beamer}
\usepackage{etex}

\usepackage{beamerthemesplit}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
%\usefonttheme{professionalfonts}
%\usepackage{times}
\usepackage{rotating}
\usepackage{tikz}
\usepackage{amsmath,cancel}
\usepackage{mathtools}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usepackage{listings}
\usepackage[]{geometry}
\usepackage{ifxetex}
\ifxetex{%
  \usepackage{fontspec}
  \setmainfont{Linux Libertine O} % or any font on your system
  \newfontfamily\quotefont[Ligatures=TeX]{Linux Libertine O} % or any font on your system
\else
  \usepackage[T1]{fontenc}
  \usepackage{libertine} % or any other font package (or none)
  \newcommand*\quotefont{\fontfamily{fxl}} % selects Libertine for quote font
\fi
\usepackage{framed}

\usepackage{soul}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.text}
\usetikzlibrary{calc,shapes.callouts,shapes.arrows}
\makeatletter

@@

\title[The ANTs Cortical Thickness Pipeline]{The ANTs Cortical Thickness Pipeline}
\author[N. Tustison]{%
  N.J. Tustison$^{1}$, B.B. Avants$^{2}$, P.A. Cook$^{2}$, G. Song$^{2}$, S. Das$^{2}$, N. van Strien$^{3}$, J.R. Stone$^{1}$, J.C. Gee$^{2}$
  }
\date[SPIE 2013:  Orlando, FL]{}
\institute[ntustison@virginia.edu]{
  $^{1}$Department of Radiology and Medical Imaging, University of Virginia \\
  $^{2}$Penn Image and Computing Science Laboratory, University of Pennsylvania \\
  $^{3}$Department of Circulation and Medical Imaging, Norwegian University of Science and Technology}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Cortical thickness uses
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Cortical thickness studies}
\begin{columns}[c]
  \begin{column}{0.45\textwidth}
    \begin{itemize}
    \item Huntington's disease
    \item schizophrenia
    \item bipolar disorder
    \item Alzheimer's disease
    \item Fronto-temporal dementia
    \item Parkinson's disease
    \item Williams syndrome
    \item multiple sclerosis
    \item autism
    \item migraines
    \item chronic smoking
    \end{itemize}
  \end{column}  
  \begin{column}{0.45\textwidth}
    \begin{itemize}
    \item alcholism
    \item cocaine addiction
    \item Tourette syndrome in children
    \item scoliosis in female adolescents
    \item obsessive compulsive disorder
    \item attention deficit hyperactivity disorder
    \item obesity
    \item heritable depression
    \item elderly depression
    \end{itemize}
  \end{column}  
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Cortical thickness uses 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Cortical thickness studies (cont.)}
\begin{columns}[c]
  \begin{column}[t]{0.45\textwidth}
    \begin{itemize}
    \item Correlated with:
      \begin{itemize}
		    \item age
		    \item gender
		    \item untreated transsexuality
		    \item handedness
		    \item intelligence
		    \item athletic ability
		    \item musical ability
		    \item tendency towards criminality
		    \item Tetris-playing ability in female adolescents
		  \end{itemize}    
    \end{itemize}
  \end{column}  
  \begin{column}[t]{0.45\textwidth}
    \begin{itemize}
     \item functional connectivity relationships
    \end{itemize}
  \end{column}  
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Motivation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Mention having a complete volumetric pipeline analogous to
% the entire Freesurfer pipeline.  Also talk about Clarkson's
% paper.

\begin{frame}{}

  \begin{center}
    \includegraphics[height=8cm]{Freesurfer.png}
   \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Materials
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Data}
\begin{columns}[c]
  \begin{column}[c]{0.4\textwidth}
      \begin{itemize}
		    \item IXI (Imperial College)
		      \begin{itemize}
		        \item 581 subjects
		        \item T1, T2, PD, DWI
		        \item 3 sites, 1.5 \& 3 T
		      \end{itemize}
		    \item Oasis (WUSTL)
		      \begin{itemize}
		        \item 416 subjects
		        \item 100 mild AD
		        \item defaced
		      \end{itemize}
		    \item NKI/Rockland
		      \begin{itemize}
		        \item 188 subjects
		        \item T1, T2, R-fMRI, DTI
		        \item defaced
		      \end{itemize}
		    \item Kirby (VU)
		      \begin{itemize}
		        \item 41 subjects
		        \item T1, T2, DTI,\ldots
		      \end{itemize}
		  \end{itemize}    
  \end{column}  
 \begin{column}[c]{0.4\textwidth}
   \begin{tabular}{cc}
     \vspace{-0.05cm}
     \includegraphics[width=1.75cm]{IXI048_axial.png} &  
     \includegraphics[width=1.75cm]{IXI048_sag.png} \\
     \vspace{-0.05cm}
     \includegraphics[width=1.75cm]{OAS1_0039_axial.png} &  
     \includegraphics[width=1.75cm]{OAS1_0039_sag.png} \\
     \vspace{-0.05cm}
     \includegraphics[width=1.75cm]{NKI_2861923_axial.png} &  
     \includegraphics[width=1.75cm]{NKI_2861923_sag.png} \\
     \vspace{-0.05cm}
     \includegraphics[width=1.75cm]{KKI2009-25_axial.png} &  
     \includegraphics[width=1.75cm]{KKI2009-25_sag.png} 
   \end{tabular}
 \end{column}
\end{columns}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Algorithms
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Algorithms}

\begin{center}
  \begin{itemize}
    \item \texttt{N4BiasFieldCorrection.cxx}\tikz[remember picture] \node (a) {\vphantom{X}};
    \item \texttt{antsRegistration.cxx}\tikz[remember picture] \node (b) {\vphantom{X}};
    \item \texttt{antsAffineInitializer.cxx}
    \item \texttt{Atropos.cxx}\tikz[remember picture] \node (c) {\vphantom{X}};
    \item \texttt{KellyKapowski.cxx}\tikz[remember picture] \node (d) {\vphantom{X}};
    \item \texttt{ImageMath.cxx}
    \item \texttt{abp.sh}
  \end{itemize}    
\end{center}

\begin{tikzpicture}[remember picture,overlay]
\path<2> (a.east) ++(0,1) node[anchor=west,ellipse callout,fill=red!50,opacity=1, callout absolute pointer={(a.mid)},text =black]  {IEEE-TMI 2010};
\end{tikzpicture}

\begin{tikzpicture}[remember picture,overlay]
\path<3> (b.east) ++(0,1) node[anchor=west,ellipse callout,fill=yellow!50,opacity=1, callout absolute pointer={(b.mid)},text =black]  {MIA 2008, IEEE-TIP 2009};
\end{tikzpicture}

\begin{tikzpicture}[remember picture,overlay]
\path<4> (c.east) ++(0,1) node[anchor=west,ellipse callout,fill=green!50,opacity=1, callout absolute pointer={(c.mid)},text =black]  {Neuroinformatics 2011};
\end{tikzpicture}

\begin{tikzpicture}[remember picture,overlay]
\path<5> (d.east) ++(0,1) node[anchor=west,ellipse callout,fill=orange!50,opacity=1, callout absolute pointer={(d.mid)},text =black]  {Neuroimage 2009};
\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  abp.sh
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lstset{frame = htb,
        framerule = 0.25pt,
        float,
        fontadjust,
        backgroundcolor={\color{black}},
        basicstyle=\fontfamily{pcr}\selectfont\tiny\color{green},
        keywordstyle = {\ttfamily\color{green}\textbf},
        identifierstyle = {\ttfamily},
        commentstyle = {\ttfamily\color{green}\textit},
        stringstyle = {\ttfamily},
        showstringspaces = false,
        showtabs = false
        numbers = none,
        numbersep = 6pt,
        numberstyle={\ttfamily\color{listnumbers}},
        tabsize = 2,
        language=bash,
        floatplacement=!h,
%        caption={Representative script used for the LPBA40 evaluation.},
        captionpos=b,
        label=listing:script
        }

\begin{frame}[fragile]
\frametitle{\texttt{abp.sh}}

\begin{lstlisting}
$ sh ~/Pkg/Utilities/scripts/abp.sh

This script, apb.sh, performs T1 anatomical brain processing where the following
steps are currently applied:

  1. Brain extraction
  2. Brain 3-tissue segmentation
  3. Cortical thickness
  4. (Optional) registration to a template

Usage:

abp.sh -d imageDimension
       -a anatomicalImage.nii.gz
       -e brainExtractionTemplate
       -m brainExtractionProbabilityMask
       -l brainSegmentationTemplate
       -p brainSegmentationPriors
       <OPTARGS>
       -o outputPrefix

Example:

  bash /Users/ntustison/Pkg/Utilities/scripts/abp.sh -d 3 -i t1.nii.gz -e brainWithSkullTemplate.nii.gz
  -m brainPrior.nii.gz -l segmentationTemplate.nii.gz -p segmentationPriors%d.nii.gz -o output

Required arguments:
   ...

Optional arguments:
   ...

\end{lstlisting}

@@

%\uncover<1->{
    \path[->,rounded corners=0.1cm] node[format, yshift=2cm, text width=1.5cm, text height=0.0cm ] (ixi) { 
        \begin{center}
			  \includegraphics[height=1.75cm]{IXI221.png} \\
        \tiny{Input MRI}
        \end{center}
			  };
    \path[->] node[format, right of=ixi, xshift=0.5cm, text width=1.25cm, text height=-0.35cm ] (n4) {
          \begin{center}
            \tiny{Initial N4 bias correction}
          \end{center}
        };
    \draw[->] (ixi.0) --  (n4.180);    
    \path[->] node[format, below of=n4, yshift = 1.25cm, text width=1.25cm, text height=-0.35cm ] (be) {
          \begin{center}
            \tiny{Brain extraction}
          \end{center}
        };
    \draw[->] (n4.-90) -- (be.90);    
    \path[->] node[format, below of=be, yshift = 1.25cm, text width=1.25cm, text height=-0.35cm ] (n4_2) {
          \begin{center}
            \tiny{N4 using WM estimate}
          \end{center}
        };
    \draw[->] (be.-90) -- (n4_2.90);    
    \path[->] node[format, below of=n4_2, yshift=1.25cm, text width=1.25cm, text height=-0.35cm ] (atropos) {
          \begin{center}
            \tiny{3-tissue segmentation}
          \end{center}
        };
    \draw[->] (n4_2.-90) -- (atropos.90);    
    \path[->] node[diamond, draw, thick, fill=middlecolour, left of=atropos, xshift=1.75cm, yshift=0.875cm, text width=0.5cm, text height=-0.65cm ] (conv) {
          \begin{center}
            \tiny{Conv.?}
          \end{center}
        };
    \draw[->] (atropos.180) -| (conv.270);    
    \draw[->] (conv.90) |- node {\tiny no} (n4_2.180);

    \path[->] node[format, left of=atropos, xshift=-0.5cm, text width=1.5cm, text height=-0.35cm  ] (kk) {
        \begin{center}
        \tiny{Cortical thickness estimation}
        \end{center}
			  };
    \path[->,rounded corners=0.1cm] node[format, above of=kk, yshift=-1cm, text width=1.5cm, text height=-0.3cm  ] (kkmap) {
        \begin{center}
			  \includegraphics[height=1.75cm]{IXI221_direct.png} \\
        \tiny{Thickness map}
        \end{center}
			  };

    \draw[->] (conv.180) -- node {\tiny yes} ([yshift=0cm,xshift=-0.45cm]conv.180) |- (kk.0);    
    \draw[<-] (kkmap.270) -- (kk.90);    
%}

%\uncover<2->{
    \path[->,rounded corners=0.1cm] 
      node[format, right of=n4, xshift=1.15cm, yshift=-2.5cm,text width=4.75cm,text height=-0.3cm  ] (template) { 
        \begin{center}
        \tiny{Oasis template (35 normals)}
        \begin{tabular}{cc}
          \includegraphics[width=1.5cm]{MICCAI_T1.png} &
          \includegraphics[width=1.5cm]{MICCAI_probMask.png} \\
          \tiny{T1} & \tiny{Whole brain} 
        \end{tabular} \\
        \begin{tabular}{ccc}
          \includegraphics[width=1.5cm]{MICCAI_probCSF.png} &
          \includegraphics[width=1.5cm]{MICCAI_probGM.png} &
          \includegraphics[width=1.5cm]{MICCAI_probWM.png} \\
          \tiny{CSF} & \tiny{GM} & \tiny{WM}
        \end{tabular} \\
        \end{center}
			  };
    \draw[->,dashed] (template.160) -- ([yshift=0cm,xshift=-0.5cm]template.160) |- (be.0); 
    \draw[->,dashed] (template.200) -- ([yshift=0cm,xshift=-0.5cm]template.200) |- (atropos.0); 
%}

%\uncover<3->{
  \node[decorate,draw,minimum height=7.25cm,minimum width=5.65cm,dashed,rounded corners=0.2cm, thin, color = yellow] (c) at (1.7,-0.35) {};
%}  
%\uncover<4->{
  \node[decorate,draw,minimum height=5.25cm,minimum width=5.55cm,dashed,rounded corners=0.2cm, thin, color = red] (c) at (7.7,-0.45) {};
%}
\end{tikzpicture}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Brain extraction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Brain extraction}

		\begin{tikzpicture}[node distance=4cm, auto,>=latex', thin]
		    % We need to set at bounding box first. Otherwise the diagram
		    % will change position for each frame.
		    \path[use as bounding box] (-1,0) rectangle (10,0);

\uncover<1->{    
		    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm, xshift=2cm,yshift=1.5cm] (nodots) { 
		        \begin{center}
       	      \includegraphics[width = 4.5cm]{nodots.pdf}
		        \end{center}
					  };
		    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm, below of=nodots, xshift=1.1cm,yshift=2.8cm] { 
		    {\scriptsize template}
		    };
		    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm, below of=nodots, xshift=3.5cm,yshift=2.8cm] { 
		    {\scriptsize subject}
		    };
}					  
\uncover<2->{    
		    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm, xshift=2cm,yshift=1.5cm] (dots) { 
		        \begin{center}
       	      \includegraphics[width = 4.5cm]{dots.pdf}
		        \end{center}
					  };
}					  
\uncover<3->{    
		    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm, text height=-0.3cm, below of = dots] (pair) { 
		        \begin{center}
		          \begin{tabular}{c}
         	      \includegraphics[width = 2.5cm]{laplacian.pdf} \\
         	      \includegraphics[width = 2.5cm]{nodots.pdf}
	            \end{tabular}
		        \end{center}
					  };
        \path[draw, -latex'] (nodots) -- node{\scriptsize Affine init.} (pair);			  
}

\uncover<4->{    
    \path[->,rounded corners=0.1cm] node[format,text width=5.5cm, right of = dots, xshift=2cm, yshift=-2cm] (fails) { 
        \begin{center}
    	      {Extraction failures} \\
     \vspace{0.5cm}
   \begin{tabular}{cc}
     \begin{sideways}\texttt{IXI\_191}\end{sideways} & \includegraphics[width=4cm]{IXI191_failure.png} \\
     \begin{sideways}\texttt{IXI\_370}\end{sideways} & \includegraphics[width=4cm]{IXI370_failure.png} \\
     \begin{sideways}\texttt{IXI\_594}\end{sideways} & \includegraphics[width=4cm]{IXI594_failure.png} 
   \end{tabular}
        \end{center}

			  };
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  N4 Atropos brain segmentation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{N4 $\leftrightarrow$ Atropos}

\uncover<1->{ 
  \path[->,rounded corners=0.1cm] node[format,text width=1.75cm, xshift = -0.35cm] (extraction) { 
      \begin{center}
          \begin{tabular}{cc}
    	        \includegraphics[width = 1.75cm]{extraction.png} &
    	        \includegraphics[width = 1.75cm]{weightmask.png} \\
	           {\scriptsize brain mask} & 
	           {\scriptsize weight mask}
	           \end{tabular}
      \end{center}
	};
}	
\uncover<2->{ 
  \path[->,rounded corners=0.1cm] 
    node[format,text width=1.75cm, yshift=2cm, xshift=1.75cm,right of=extraction] (n4) { 
      \begin{center}
        \includegraphics[width = 1.75cm]{n4.png} \\
        {\scriptsize N4}
      \end{center}
	};
  \path[->,thick] (extraction.45) edge [out=45, in=180] (n4.180);			  
}  
\uncover<3->{ 
  \path[->,rounded corners=0.1cm] 
    node[format,text width=1.75cm, yshift=-2cm, right of=n4] (atropos) { 
      \begin{center}
        \includegraphics[width = 1.75cm]{segmentation.png} \\
	        {\scriptsize Atropos}
      \end{center}
	};
  \path[->,thick] (n4.0) edge [out=0, in=135] (atropos.90);			  
}

\uncover<4->{ 
  \path[->,rounded corners=0.1cm] 
    node[format,text width=2.5cm, below of=n4] (conv) { 
      \begin{center}
        \includegraphics[width = 2.5cm]{convergence.pdf} \\
	        {\scriptsize Convergence?}
      \end{center}
	};
  \path[->,thick] (atropos.-90) edge [out=-135, in=0] (conv.0);			  
}

\uncover<5->{ 
  \path[->,thick] (conv.180) edge [out=180, in=-45] (extraction.-45);			  
  \draw[->,thick,dashed] (atropos.180) -- node {\scriptsize update weight mask} ([xshift=1.75cm]extraction.0);			  
}

\end{tikzpicture}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  DiReCT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{frame}{DiReCT}
%
%\end{frame}

@@
